Manuscript analyses

### 2025-02-12 cilta_cel/Severe infection table.Rmd
Add additional analyses

```{r exploratory function}
# check_data <- function(data){
#   
#   for(i in 1:length(colnames(data))) {
#     
#     if(class(data[[i]]) == "factor" | class(data[[i]]) == "character") {
#       
#       # print(data[i])
#       print(colnames(data[i]))
#       print(table(data[[i]]))
#     }
#     
#   }
# }
# 
# check_data(cart[2:50])
# check_data(cart[51:100])
# check_data(cart[101:150])
# check_data(cart[151:200]) # has < : "CRP Pre-Leukapheresis", 
# check_data(cart[201:250]) # has < :"CRP day +21",  "CRP day +30", 
# # has > :  "CRP day +90"
# check_data(cart[251:300]) # has < : "CRP day +180"
# check_data(cart[1:44, 301:353]) # need to see patient in Moffitt
```

@@

### Tables
Patients evaluable at each time point
```{r evaluable}
day7 <- cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  filter(pfs_event == 0 | pfs_from_infusion_months > (7 / 30.417)) %>% 
  select(pt_identifier) %>% 
  tbl_summary(missing = "no") %>% 
  bold_labels() %>% add_stat_label()
day14 <- cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  filter(pfs_event == 0 | pfs_from_infusion_months > (14 / 30.417)) %>% 
  select(pt_identifier) %>% 
  tbl_summary(missing = "no") %>% 
  bold_labels() %>% add_stat_label()
day21 <- cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  filter(pfs_event == 0 | pfs_from_infusion_months > (21 / 30.417)) %>% 
  select(pt_identifier) %>% 
  tbl_summary(missing = "no") %>% 
  bold_labels() %>% add_stat_label()
day30 <- cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  filter(pfs_event == 0 | pfs_from_infusion_months > (30 / 30.417)) %>% 
  select(pt_identifier) %>% 
  tbl_summary(missing = "no") %>% 
  bold_labels() %>% add_stat_label()
day90 <- cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  filter(pfs_event == 0 | pfs_from_infusion_months > 3) %>% 
  select(pt_identifier) %>% 
  tbl_summary(missing = "no") %>% 
  bold_labels() %>% add_stat_label()
day180 <- cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  filter(pfs_event == 0 | pfs_from_infusion_months > 6) %>% 
  select(pt_identifier) %>% 
  tbl_summary(missing = "no") %>% 
  bold_labels() %>% add_stat_label()
mon12 <- cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  filter(pfs_event == 0 | pfs_from_infusion_months > 12) %>% 
  select(pt_identifier) %>% 
  tbl_summary(missing = "no") %>% 
  bold_labels() %>% add_stat_label()
tbl_merge(list(day7, day14, day21, day30, day90, day180, mon12), 
          tab_spanner = c("day7", "day14", "day21", "day30", "day90", "day180", "month12"))
```

```{r infused}
cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  select(`infused?` = notinfused) %>% 
  tbl_summary(missing = "no") %>% 
  bold_labels() %>% add_stat_label()
```

```{r death}
cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  mutate(os_event = case_when(
    os_event == 1          ~ "Died",
    os_event == 0          ~ "Alive"
  )) %>% 
  select(os_event) %>% 
  tbl_summary() %>% 
  bold_labels() %>% add_stat_label()

cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  filter(os_event == 1) %>% 
  select(`cause of death` = cause_of_death_myeloma_toxicitiy_unrelated) %>% 
  tbl_summary() %>% 
  bold_labels() %>% add_stat_label()
```

## Table 1. Patient baseline characteristics
```{r Table 1}
cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  select(os_from_infusion_months, age, agecat, male_sex, sex,
         extramedullary_disease_yes_no, 
         high_marrow_burden_50_percent, ecog_at_ld, 
         r_iss_at_car_t_infusion, 
         cytogenetics, cytogenetics_incl_1q,
         deletion_17p_prior_to_car_t_infusion_yes_no,
         t_4_14_prior_to_car_t_infusion_yes_no,
         t_14_16_prior_to_car_t_infusion_yes_no, gain_amp1q21,
         bridging_therapy_yes_no,
         # `Received alkylating therapy with bridging (Yes=1, No=0)`,
         prior_auto_sct_yes_no, prior_allo_sct_within_6_months_before_apheresis,
         Prior_bcma_therapy,
         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
         did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no,
         ht_score, early_icaht_cat, any_early_icaht,
         gr3_early_icaht, 
         late_icaht_cat, any_late_icaht,
         gr3_late_icaht) %>% 
  tbl_summary(
    type = list(
      c(agecat, sex, 
        extramedullary_disease_yes_no, high_marrow_burden_50_percent,
        cytogenetics, cytogenetics_incl_1q,
        deletion_17p_prior_to_car_t_infusion_yes_no,
        t_4_14_prior_to_car_t_infusion_yes_no,
        t_14_16_prior_to_car_t_infusion_yes_no, gain_amp1q21,
        bridging_therapy_yes_no, prior_auto_sct_yes_no,
        Prior_bcma_therapy,
        # `Received alkylating therapy with bridging (Yes=1, No=0)`,
        immuno, proteasome, dara, doubleref, tripleref, pentaref,
        did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no,
        ht_score, early_icaht_cat, any_early_icaht,
         gr3_early_icaht, 
         late_icaht_cat, any_late_icaht,
         gr3_late_icaht)
      ~"categorical"),

    statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
    digits = all_continuous() ~ 1
  ) %>% 
  bold_labels() %>% add_stat_label() %>% 
  modify_footnote(update = everything() ~ NA)
```

## Table 2. Clinical outcomes
```{r}
tbl1 <- cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  select(max_crs_grade_0_5, CRS_gradecat,
         day_of_onset_crs_relative_to_infusion,
         day_of_max_crs_relative_to_infusion,
         duration_of_crs_days, 
         max_icans, ICANS_gradecat,
         day_of_onset_icans_relative_to_infusion,
         day_of_max_icans_relative_to_infusion,
         duration_of_icans_days,
         delayed_neuro,
         parkinsonian_neurotoxicity_yes_no,
         other_delayed_non_parkinsonian_neurologic_toxicity_yes_no,
         delayed_neuro_type,
         hlh, hlh_hlh_like_toxicities,
         overall_hlh) %>% 
  tbl_summary(type = list(
    c(day_of_onset_crs_relative_to_infusion,
      day_of_max_crs_relative_to_infusion,
      duration_of_crs_days,
      day_of_onset_icans_relative_to_infusion,
      day_of_max_icans_relative_to_infusion,
      duration_of_icans_days) ~ "continuous",
    c(delayed_neuro,
      parkinsonian_neurotoxicity_yes_no,
      other_delayed_non_parkinsonian_neurologic_toxicity_yes_no,
      hlh, hlh_hlh_like_toxicities,
      overall_hlh) 
    ~ "categorical"),
    statistic=list(all_continuous() ~ "{median} ({min}, {max})"),
    digits = all_continuous() ~ 1,
    missing = "no"
    ) %>% 
  bold_labels() %>% add_stat_label()

tbl2 <- cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  select(steroid_use_yes_no, tocilizumab_yes_no, 
         anakinra_yes_no) %>% 
  tbl_summary(type = list(
    c(steroid_use_yes_no, tocilizumab_yes_no, 
      anakinra_yes_no) ~ "categorical"),
    statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
    digits = all_continuous() ~ 1
    ) %>% 
  bold_labels() %>% add_stat_label()

tbl3 <- cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  select(MRD_day30,
         ORR_30days,
         day30_response,
         day30_response_v2) %>% 
  tbl_summary(type = list(
    c(MRD_day30) ~ "categorical"),
    digits = all_continuous() ~ 1,
    missing = "no") %>% 
  bold_labels() %>% add_stat_label()

tbl4 <- cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  filter(day30_response_v2 == "sCR or CR") %>% 
  select(MRD_day30) %>% 
  tbl_summary(type = list(
    c(MRD_day30) ~ "categorical"),
    label = list(MRD_day30 ~ 
                   "MRD_day30 within CR/sCR"),
    digits = all_continuous() ~ 1,
    missing = "no") %>% 
  bold_labels() %>% add_stat_label()

tbl5 <- cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  select(MRD_mon3,
         ORR_mon3,
         mon3_response,
         mon3_response_v2) %>% 
  tbl_summary(type = list(
    c(MRD_mon3) ~ "categorical"),
    digits = all_continuous() ~ 1,
    missing = "no") %>% 
  bold_labels() %>% add_stat_label()

tbl6 <- cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  filter(mon3_response_v2 == "sCR or CR") %>% 
  select(MRD_mon3) %>% 
  tbl_summary(type = list(c(MRD_mon3) ~ "categorical"),
              label = list(MRD_mon3 ~ "MRD_mon3 within CR/sCR"),
              digits = all_continuous() ~ 1,
              missing = "no") %>% 
  bold_labels() %>% add_stat_label()

tbl7 <- cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  select(ORR_as_best_response, best_ORRcollapsed,
         best_response, best_response_MRD) %>% 
  tbl_summary(#type = list(c(MRD_mon3) ~ "categorical"),
              # label = list(best_response ~ "best response in the first 90 days"),
              digits = all_continuous() ~ 1,
              missing = "no") %>% 
  bold_labels() %>% add_stat_label()

tbl8 <- cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  filter(best_response == "sCR or CR") %>% 
  select(best_response_MRD) %>% 
  tbl_summary(type = list(c(best_response_MRD) ~ "categorical"),
              label = list(best_response_MRD ~ "best_response_MRD within CR/sCR"),
              statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
              digits = all_continuous() ~ 1,
              missing = "no") %>% 
  bold_labels() %>% add_stat_label()

tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6, tbl7, tbl8)) #%>% as_gt() #%>%
  # gt::tab_source_note(gt::md("**At 30days: <br>
  #                            1 patient is not evaluable by IMWG - non-secretory disease, including no bone marrow involvement; <br>
  #                            1 patients was not evaluated. <br>
  #                            At 90days: <br>
  #                            1 patient is not evaluable by IMWG - non-secretory disease, including no bone marrow involvement; <br>
  #                            1 patient is not Heme not evaluable; <br>
  #                            2 patients were not evaluated; <br>
  #                            1 patients is not evaluable by death**"))

@@

<!-- For responses make denominator evaluable patients -->
<!-- Patient who died or was lost to follow-up or had non-secretory disease would not be evaluable -->

## Table S3. Apheresis and product characteristics
```{r Apheresis and product characteristics}
cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  select(tbv, whole_blood_processed_m_l,
         final_collection_volume_m_l, 
         tbv_processed, 
         access_type,
         run_time_min,
         time_from_apheresis_to_car_t_infusion_days, total_bags,
         total_dose_volume_m_l, cell_dose_million_cells
  ) %>% 
  tbl_summary(type = list(
    c(tbv, total_bags) ~ "continuous"),
    statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
    digits = all_continuous() ~ 1,
  missing = "no") %>% 
  bold_labels() %>% add_stat_label()
```

## Table 3 A-B. Cytopenias following cilta-cel
Evaluable patients (who survived and did not progressed) are included for each time points.
```{r Table 3}
tbl1 <- cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  select("Leukopenia" = Leukopenia_apheresis, 
         "Grade3+ Leukopenia" = gr3_Leukopenia_apheresis, 
         "Neutropenia" = Neutropenia_apheresis, 
         "Grade3+ Neutropenia" = gr3_Neutropenia_apheresis, 
         "Anemia" = Anemia_apheresis, 
         "Grade3+ Anemia" = gr3_Anemia_apheresis, 
         "Thrombocytopenia" = Thrombocytopenia_apheresis, 
         "Grade3+ Thrombocytopenia" = gr3_Thrombocytopenia_apheresis,
         "Any Cytopenia" = cytopenia_apheresis,
         "Grade3+ Cytopenia" = gr3_cytopenia_apheresis
  ) %>% 
  tbl_summary(type = list(everything() ~ "dichotomous"),
              digits = all_continuous() ~ 1,
              missing = "no"
  ) %>% 
  bold_labels() %>% add_stat_label()

tbl2 <- cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  select("Leukopenia" = `Leukopenia_-5d`, 
         "Grade3+ Leukopenia" = `gr3_Leukopenia_-5d`, 
         "Neutropenia" = `Neutropenia_-5d`, 
         "Grade3+ Neutropenia" = `gr3_Neutropenia_-5d`,
         "Anemia" = `Anemia_-5d`, 
         "Grade3+ Anemia" = `gr3_Anemia_-5d`, 
         "Thrombocytopenia" = `Thrombocytopenia_-5d`, 
         "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_-5d`,
         "Any Cytopenia" = `cytopenia_-5d`,
         "Grade3+ Cytopenia" = `gr3_cytopenia_-5d`
  ) %>% 
  tbl_summary(type = list(everything() ~ "dichotomous"),
              digits = all_continuous() ~ 1,
              missing = "no"
  ) %>% 
  bold_labels() %>% add_stat_label()

tbl3 <- cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  select("Leukopenia" = Leukopenia_0d, 
         "Grade3+ Leukopenia" = gr3_Leukopenia_0d, 
         "Neutropenia" = Neutropenia_0d, 
         "Grade3+ Neutropenia" = gr3_Neutropenia_0d, 
         "Anemia" = Anemia_0d, 
         "Grade3+ Anemia" = gr3_Anemia_0d,
         "Thrombocytopenia" = Thrombocytopenia_0d, 
         "Grade3+ Thrombocytopenia" = gr3_Thrombocytopenia_0d,
         "Any Cytopenia" = cytopenia_0d,
         "Grade3+ Cytopenia" = gr3_cytopenia_0d
  ) %>% 
  tbl_summary(type = list(everything() ~ "dichotomous"),
              digits = all_continuous() ~ 1,
              missing = "no"
  ) %>% 
  bold_labels() %>% add_stat_label()

tbl4 <- cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  filter(pfs_event == 0 | pfs_from_infusion_months > (7 / 30.417)) %>% 
  select("Leukopenia" = Leukopenia_7d, 
         "Grade3+ Leukopenia" = gr3_Leukopenia_7d, 
         "Neutropenia" = Neutropenia_7d, 
         "Grade3+ Neutropenia" = gr3_Neutropenia_7d, 
         "Anemia" = Anemia_7d, 
         "Grade3+ Anemia" = gr3_Anemia_7d, 
         "Thrombocytopenia" = Thrombocytopenia_7d, 
         "Grade3+ Thrombocytopenia" = gr3_Thrombocytopenia_7d,
         "Any Cytopenia" = cytopenia_7d,
         "Grade3+ Cytopenia" = gr3_cytopenia_7d
  ) %>% 
  tbl_summary(type = list(everything() ~ "dichotomous"),
              digits = all_continuous() ~ 1,
              missing = "no"
  ) %>% 
  bold_labels() %>% add_stat_label()

tbl5 <- cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  filter(pfs_event == 0 | pfs_from_infusion_months > (14 / 30.417)) %>% 
select("Leukopenia" = Leukopenia_14d, 
       "Grade3+ Leukopenia" = gr3_Leukopenia_14d, 
       "Neutropenia" = Neutropenia_14d, 
       "Grade3+ Neutropenia" = gr3_Neutropenia_14d,
       "Anemia" = Anemia_14d, 
       "Grade3+ Anemia" = gr3_Anemia_14d,
       "Thrombocytopenia" = Thrombocytopenia_14d, 
       "Grade3+ Thrombocytopenia" = gr3_Thrombocytopenia_14d,
       "Any Cytopenia" = cytopenia_14d,
       "Grade3+ Cytopenia" = gr3_cytopenia_14d
) %>% 
  tbl_summary(type = list(everything() ~ "dichotomous"),
              digits = all_continuous() ~ 1,
              missing = "no"
  ) %>% 
  bold_labels() %>% add_stat_label()

tbl6 <- cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  filter(pfs_event == 0 | pfs_from_infusion_months > (21 / 30.417)) %>% 
  select("Leukopenia" = Leukopenia_21d,
         "Grade3+ Leukopenia" = gr3_Leukopenia_21d, 
         "Neutropenia" = Neutropenia_21d, 
         "Grade3+ Neutropenia" = gr3_Neutropenia_21d, 
         "Anemia" = Anemia_21d, 
         "Grade3+ Anemia" = gr3_Anemia_21d,
         "Thrombocytopenia" = Thrombocytopenia_21d, 
         "Grade3+ Thrombocytopenia" = gr3_Thrombocytopenia_21d,
         "Any Cytopenia" = cytopenia_21d,
         "Grade3+ Cytopenia" = gr3_cytopenia_21d
  ) %>% 
  tbl_summary(type = list(everything() ~ "dichotomous"),
              digits = all_continuous() ~ 1,
              missing = "no"
  ) %>% 
  bold_labels() %>% add_stat_label()

tbl7 <- cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  filter(pfs_event == 0 | pfs_from_infusion_months > (30 / 30.417)) %>% 
  select("Leukopenia" = Leukopenia_30d, 
         "Grade3+ Leukopenia" = gr3_Leukopenia_30d,
         "Neutropenia" = Neutropenia_30d, 
         "Grade3+ Neutropenia" = gr3_Neutropenia_30d,
         "Anemia" = Anemia_30d, 
         "Grade3+ Anemia" = gr3_Anemia_30d, 
         "Thrombocytopenia" = Thrombocytopenia_30d,
         "Grade3+ Thrombocytopenia" = gr3_Thrombocytopenia_30d,
         "Any Cytopenia" = cytopenia_30d,
         "Grade3+ Cytopenia" = gr3_cytopenia_30d
  ) %>% 
  tbl_summary(type = list(everything() ~ "dichotomous"),
              digits = all_continuous() ~ 1,
              missing = "no"
  ) %>% 
  bold_labels() %>% add_stat_label()

tbl8 <- cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  filter(pfs_event == 0 | pfs_from_infusion_months > 3) %>% 
  select("Leukopenia" = Leukopenia_90d, 
         "Grade3+ Leukopenia" = gr3_Leukopenia_90d,
         "Neutropenia" = Neutropenia_90d, 
         "Grade3+ Neutropenia" = gr3_Neutropenia_90d,
         "Anemia" = Anemia_90d,
         "Grade3+ Anemia" = gr3_Anemia_90d,
         "Thrombocytopenia" = Thrombocytopenia_90d, 
         "Grade3+ Thrombocytopenia" = gr3_Thrombocytopenia_90d,
         "Any Cytopenia" = cytopenia_90d,
         "Grade3+ Cytopenia" = gr3_cytopenia_90d
  ) %>% 
  tbl_summary(type = list(everything() ~ "dichotomous"),
              digits = all_continuous() ~ 1,
              missing = "no"
  ) %>% 
  bold_labels() %>% add_stat_label()

tbl9 <- cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  filter(pfs_event == 0 | pfs_from_infusion_months > 6) %>% 
  select("Leukopenia" = Leukopenia_180d, 
         "Grade3+ Leukopenia" = gr3_Leukopenia_180d,
         "Neutropenia" = Neutropenia_180d, 
         "Grade3+ Neutropenia" = gr3_Neutropenia_180d,
         "Anemia" = Anemia_180d,
         "Grade3+ Anemia" = gr3_Anemia_180d,
         "Thrombocytopenia" = Thrombocytopenia_180d, 
         "Grade3+ Thrombocytopenia" = gr3_Thrombocytopenia_180d,
         "Any Cytopenia" = cytopenia_180d,
         "Grade3+ Cytopenia" = gr3_cytopenia_180d
  ) %>% 
  tbl_summary(type = list(everything() ~ "dichotomous"),
              digits = all_continuous() ~ 1,
              missing = "no"
  ) %>% 
  bold_labels() %>% add_stat_label()

tbl_merge(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6, tbl7, tbl8, tbl9), 
          tab_spanner = c("Apheresis", "Day -5", "Day 0", 
                          "Day 7", "Day 14", "Day 21",
                          "Day 30", "Day 90", "Day 180")) # %>% as_gt() #%>%
# gt::tab_source_note(gt::md("**Not evaluable patients are removed from the denominator <br>
#                            1 patient has missing 90 days values**"))
```
<br>

```{r}
tbl1 <- cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  select(any_early_icaht, 
         gr3_early_icaht, 
         any_late_icaht, 
         gr3_late_icaht
  ) %>% 
  tbl_summary(type = list(everything() ~ "dichotomous"),
              digits = all_continuous() ~ 1,
              missing = "no"
  ) %>% 
  bold_labels() %>% add_stat_label()

tbl2 <- cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  select(any_early_icaht, 
         gr3_early_icaht, 
         any_late_icaht, 
         gr3_late_icaht
  ) %>% 
  tbl_summary(type = list(everything() ~ "dichotomous"),
              digits = all_continuous() ~ 1,
              missing = "no"
  ) %>% 
  bold_labels() %>% add_stat_label()

>>>>

@@

```{r}
cilta <- cilta %>% 
  mutate(infection_type_bacterial_viral_fungal_parasitic = 
           factor(infection_type_bacterial_viral_fungal_parasitic, 
                  levels = c("Bacterial", "Fungal", "Viral")))
```

# Any infection
85 infection that you separated into 88 in 51 patients
```{r}
cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>%
  select("Patient with infection" = any_infection) %>% 
  tbl_summary() %>% 
  bold_levels() %>% 
  modify_header(update = all_stat_cols() ~ "Overall number of patient = {n}")

cilta %>% 
  select("Overall number of infection"= any_infection) %>% 
  tbl_summary() %>% 
  bold_levels() %>% 
  modify_header(update = all_stat_cols() ~ "**{level}**")
```

6 patients experienced infection in the first 30 days then had another infection between days 31 and 100
```{r}
infection_30days <- cilta %>% 
  filter(time_from_infusion_to_infection_days <= 30) %>% 
  filter(any_infection == "Yes")

cilta %>% 
  filter(time_from_infusion_to_infection_days > 30 &
           time_from_infusion_to_infection_days <= 100) %>% 
  filter(any_infection == "Yes") %>% 
  filter(pt_identifier %in% c(infection_30days$pt_identifier)) %>% 
  select(pt_identifier) %>% 
  distinct() %>% 
  tbl_summary()

@@

# In the first 30 days after cilta-cel, 30 infections occurred in 23 patients; 15 severe infections occurred in 9 patients
```{r}
cilta %>% 
  filter(time_from_infusion_to_infection_days <= 30) %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>%
  select(any_infection) %>% 
  tbl_summary(statistic = everything() ~ "{n}",
              label = list(any_infection = "Patient with infection"),
              type = list(any_infection ~ "dichotomous"),
              value = list(any_infection ~ "Yes")) %>% 
  bold_labels() %>% 
  modify_header(update = all_stat_cols() ~ "**{level}**")

cilta %>% 
  filter(time_from_infusion_to_infection_days <= 30) %>% 
  select(any_infection) %>% 
  tbl_summary(statistic = everything() ~ "{n}",
              label = list(any_infection = "Overall infection"),
              type = list(any_infection ~ "dichotomous"),
              value = list(any_infection ~ "Yes")) %>% 
  bold_labels() %>% 
  modify_header(update = all_stat_cols() ~ "**{level}**")

cilta %>% 
  filter(time_from_infusion_to_infection_days <= 30) %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>%
  select(any_sevinfection) %>% 
  tbl_summary(statistic = everything() ~ "{n}",
              label = list(any_sevinfection = "Patient with severe infection"),
              type = list(any_sevinfection ~ "dichotomous"),
              value = list(any_sevinfection ~ "Yes")) %>% 
  bold_labels() %>% 
  modify_header(update = all_stat_cols() ~ "**{level}**")

cilta %>% 
  filter(time_from_infusion_to_infection_days <= 30) %>% 
  select(any_sevinfection) %>% 
  tbl_summary(statistic = everything() ~ "{n}",
              label = list(any_sevinfection = "Overall severe infection"),
              type = list(any_sevinfection ~ "dichotomous"),
              value = list(any_sevinfection ~ "Yes")) %>% 
  bold_labels() %>% 
  modify_header(update = all_stat_cols() ~ "**{level}**")
```

Between days 31 and 100, 32 infections occurred in 24 patients, with __ severe infections all in different patients
```{r}
infection_patient_31_100 <- cilta %>% 
  filter(time_from_infusion_to_infection_days > 30 &
           time_from_infusion_to_infection_days <= 100) %>% 
  distinct(pt_identifier, .keep_all = TRUE)
infection_patient_31_100 %>%
  select(any_infection) %>% 
  tbl_summary(statistic = everything() ~ "{n}",
              label = list(any_infection = "Patient with infection"),
              type = list(any_infection ~ "dichotomous"),
              value = list(any_infection ~ "Yes")) %>% 
  bold_labels() %>% 
  modify_header(update = all_stat_cols() ~ "**{level}**")

cilta %>% 
  filter(time_from_infusion_to_infection_days > 30 &
           time_from_infusion_to_infection_days <= 100) %>% 
  select(any_infection) %>% 
  tbl_summary(statistic = everything() ~ "{n}",
              label = list(any_infection = "Overall infection"),
              type = list(any_infection ~ "dichotomous"),
              value = list(any_infection ~ "Yes")) %>% 
  bold_labels() %>% 
  modify_header(update = all_stat_cols() ~ "**{level}**")

cilta %>% 
filter(time_from_infusion_to_infection_days > 30 &
           time_from_infusion_to_infection_days <= 100) %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>%
  select(any_sevinfection) %>% 
  tbl_summary(statistic = everything() ~ "{n}",
              label = list(any_sevinfection = "Patient with severe infection"),
              type = list(any_sevinfection ~ "dichotomous"),
              value = list(any_sevinfection ~ "Yes")) %>% 
  bold_labels() %>% 
  modify_header(update = all_stat_cols() ~ "**{level}**")

cilta %>% 
filter(time_from_infusion_to_infection_days > 30 &
           time_from_infusion_to_infection_days <= 100) %>% 
  select(any_sevinfection) %>% 
  tbl_summary(statistic = everything() ~ "{n}",
              label = list(any_sevinfection = "Overall severe infection"),
              type = list(any_sevinfection ~ "dichotomous"),
              value = list(any_sevinfection ~ "Yes")) %>% 
  bold_labels() %>% 
  modify_header(update = all_stat_cols() ~ "**{level}**")
```

After day 100, 23 infections occurred in 17 patients, with __ severe infections all in different patients
```{r}
infection_patient_31_100 <- cilta %>% 
  filter(time_from_infusion_to_infection_days > 100) %>% 
  distinct(pt_identifier, .keep_all = TRUE)
infection_patient_31_100 %>%
  select(any_infection) %>% 
  tbl_summary(statistic = everything() ~ "{n}",
              label = list(any_infection = "Patient with infection"),
              type = list(any_infection ~ "dichotomous"),
              value = list(any_infection ~ "Yes")) %>% 
  bold_labels() %>% 
  modify_header(update = all_stat_cols() ~ "**{level}**")

cilta %>% 
  filter(time_from_infusion_to_infection_days > 100) %>% 
  select(any_infection) %>% 
  tbl_summary(statistic = everything() ~ "{n}",
              label = list(any_infection = "Overall infection"),
              type = list(any_infection ~ "dichotomous"),
              value = list(any_infection ~ "Yes")) %>% 
  bold_labels() %>% 
  modify_header(update = all_stat_cols() ~ "**{level}**")

cilta %>% 
  filter(time_from_infusion_to_infection_days > 100) %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>%
  select(any_sevinfection) %>% 
  tbl_summary(statistic = everything() ~ "{n}",
              label = list(any_sevinfection = "Patient with severe infection"),
              type = list(any_sevinfection ~ "dichotomous"),
              value = list(any_sevinfection ~ "Yes")) %>% 
  bold_labels() %>% 
  modify_header(update = all_stat_cols() ~ "**{level}**")

cilta %>% 
  filter(time_from_infusion_to_infection_days > 100) %>% 
  select(any_sevinfection) %>% 
  tbl_summary(statistic = everything() ~ "{n}",
              label = list(any_sevinfection = "Overall severe infection"),
              type = list(any_sevinfection ~ "dichotomous"),
              value = list(any_sevinfection ~ "Yes")) %>% 
  bold_labels() %>% 
  modify_header(update = all_stat_cols() ~ "**{level}**")
```

Any severe infection
28 infection that you will probably separate into more type. The next table should help you with that.
```{r}
cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>%
  select("Patient with severe infection" = any_sevinfection) %>% 
  tbl_summary() %>% 
  bold_levels() %>% 
  modify_header(update = all_stat_cols() ~ "Overall number of patient = {n}")

cilta %>% 
  select("Overall number of severe infection"= any_sevinfection) %>% 
  tbl_summary() %>% 
  bold_levels() %>% 
  modify_header(update = all_stat_cols() ~ "**{level}**")
```

## Details of severe infections after cilta-cel
```{r severe infection details 30 first days}
tbl1 <- cilta %>% 
  filter(time_from_infusion_to_infection_days <= 30) %>% 
  filter(any_sevinfection == "Yes") %>% 
  select(infection_type_bacterial_viral_fungal_parasitic) %>% 
  tbl_summary() %>%
  remove_row_type(variables = infection_type_bacterial_viral_fungal_parasitic,
                  type= "level",
                  level_value = "Fungal") %>%
  remove_row_type(variables = infection_type_bacterial_viral_fungal_parasitic,
                  type= "level",
                  level_value = "Viral") %>%
  remove_row_type(infection_type_bacterial_viral_fungal_parasitic, type = "header") %>%
  add_stat_label(label = infection_type_bacterial_viral_fungal_parasitic ~ c("n (%)"), location = "column") %>%
  modify_column_indent(columns = label, undo = TRUE) %>% 
  bold_levels() %>% 
  modify_header(update = all_stat_cols() ~ "**{level}**, N = {n}") %>%
  modify_spanning_header(all_stat_cols() ~ "**Infections in the first 30 days**")

tbl1_1 <- cilta %>% 
  filter(time_from_infusion_to_infection_days <= 30) %>% 
  filter(any_sevinfection == "Yes") %>% 
  filter(infection_type_bacterial_viral_fungal_parasitic == "Bacterial") %>%
  select(infection_type_details) %>% 
  tbl_summary(statistic = infection_type_details ~ c("{n}")) %>% 
  remove_row_type(infection_type_details, type = "header")

tbl2 <- cilta %>% 
  filter(time_from_infusion_to_infection_days <= 30) %>% 
  filter(any_sevinfection == "Yes") %>% 
  select(infection_type_bacterial_viral_fungal_parasitic) %>% 
  tbl_summary() %>%
  remove_row_type(variables = infection_type_bacterial_viral_fungal_parasitic,
                  type= "level",
                  level_value = "Bacterial") %>% 
  remove_row_type(variables = infection_type_bacterial_viral_fungal_parasitic,
                  type= "level",
                  level_value = "Viral") %>% 
  remove_row_type(infection_type_bacterial_viral_fungal_parasitic, type = "header") %>% 
  add_stat_label(label = infection_type_bacterial_viral_fungal_parasitic ~ c("n (%)"), location = "column") %>%
  bold_levels() %>%
  modify_column_indent(columns = label, undo = TRUE)

tbl2_1 <- cilta %>% 
  filter(time_from_infusion_to_infection_days <= 30) %>% 
  filter(any_sevinfection == "Yes") %>% 
  filter(infection_type_bacterial_viral_fungal_parasitic == "Fungal") %>%
  select(infection_type_details) %>% 
  tbl_summary(statistic = infection_type_details ~ c("{n}")) %>% 
  remove_row_type(infection_type_details, type = "header")

tbl3 <- cilta %>% 
  filter(time_from_infusion_to_infection_days <= 30) %>% 
  filter(any_sevinfection == "Yes") %>% 
  select(infection_type_bacterial_viral_fungal_parasitic) %>% 
  tbl_summary() %>%
  remove_row_type(variables = infection_type_bacterial_viral_fungal_parasitic,
                  type= "level",
                  level_value = "Bacterial") %>% 
  remove_row_type(variables = infection_type_bacterial_viral_fungal_parasitic,
                  type= "level",
                  level_value = "Fungal") %>% 
  remove_row_type(infection_type_bacterial_viral_fungal_parasitic, type = "header") %>% 
  add_stat_label(label = infection_type_bacterial_viral_fungal_parasitic ~ c("n (%)"), location = "column") %>%
  bold_levels() %>%
  modify_column_indent(columns = label, undo = TRUE)

tbl3_1 <- cilta %>% 
  filter(time_from_infusion_to_infection_days <= 30) %>% 
  filter(any_sevinfection == "Yes") %>% 
  filter(infection_type_bacterial_viral_fungal_parasitic == "Viral") %>%
  select(infection_type_details) %>% 
  tbl_summary(statistic = infection_type_details ~ c("{n}")) %>% 
  remove_row_type(infection_type_details, type = "header")
